% -*- coding: utf-8 -*-

\begin{thebibliography}{OMFG42}

\input{zz_bibmacros}

\raggedright\small

\bibitem[85M85]{85m85}
  \Work{{Macscheme} Reference Manual}
  \From{Semantic Microsystems}
  \Published{Sausalito, California}{1985}

\bibitem[All78]{all78}
  \By{John~Allen}
  \Book{Anatomy of {Lisp}}
  \Published{McGraw-Hill}{1978}
  \Numpages{464}
  \Series{Computer Science Series}

\bibitem[ALQ95]{alq95}
  \By{S.~Anglade, J.-J.~Lacrampe, and C.~Queinnec}
  \Work{Semantics of Combinations in {Scheme}}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1994}
  \IssueVN{7}{4}
  \Pages{15--20}

\bibitem[App87]{app87}
  \By{Andrew~Appel}
  \Work{Garbage Collection Can Be Faster Than Stack Allocation}
  \In{Information Processing Letters}
  \At{1987}
  \IssueVN{25}{4}
  \Pages{275--279}

\bibitem[App92a]{app92a}
  \By{Andrew~Appel}
  \Book{Compiling with Continuations}
  \Published{Cambridge Press}{1992}
  \Numpages{272}

\bibitem[App92b]{app92b}
  \Work{{Dylan}, an Object-Oriented Dynamic Language}
  \From{Apple Computer Eastern Research~{\&} Technology}
  \Published{Apple Computer, Inc.}{1992}

\bibitem[AR88]{ar88}
  \By{N.~Adams and J.~Rees}
  \Work{Object-Oriented Programming in {Scheme}}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{277--288}

\bibitem[AS85]{as85}
  \By{Harold~Abelson and Gerald~Jay~Sussman with Julie~Sussman}
  \Book{Structure and Interpretation of Computer Programs}
  \Published{MIT Press}{1985}
  \Numpages{400}

\bibitem[AS85$'$]{as85-r}
  \By{Харольд~Абельсон и Джеральд~Джей~Сассмен}
  \Book{Структура и интерпретация компьютерных программ}
  \Published{Добросвет}{2010}
  \Numpages[с.]{608}

\bibitem[AS94]{as94}
  \Work{An~Empirical and Analitical Study of Stack vs Heap Cost for Languages
        with Closures}
  \Report{technical report}{CS-TR-450-94}
  \OfPeopleFrom{Princeton University,
                Dept. of Computer Science}{A.~Appel and Zh.~Shao}
  \At{1994}

\bibitem[Att95]{att95}
  \By{Giuseppe~Attardi}
  \Work{The~Embeddable Common Lisp}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1995}
  \IssueVN{8}{1}
  \Pages{30--41}

\bibitem[Bak]{bak95}
  \By{Henry~G.~Baker}
  \Work{CONS Should Not CONS Its Arguments, Part~II: Cheney on the M.T.A.}
  \In{{ACM SIGPLAN} Notices}
  \At{1995}
  \IssueVN{30}{9}
  \Pages{17--20}

\bibitem[Bak78]{bak78}
  \By{Henry~G.~Baker}
  \Work{List Processing in Real Time on a Serial Computer}
  \In{Communications of the {ACM}}
  \At{1978}
  \IssueVN{21}{4}
  \Pages{280--294}

\bibitem[Bak92a]{bak92a}
  \By{Henry~G.~Baker}
  \Work{The~Buried Binding and Dead Binding Problems of {Lisp~1.5}}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1992}
  \IssueVN{5}{2}
  \Pages{11--19}

\bibitem[Bak92b]{bak92b}
  \By{Henry~G.~Baker}
  \Work{Inlining Semantics for Subroutines Which Are Recursive}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1992}
  \IssueVN{27}{12}
  \Pages{39--46}

\bibitem[Bak92c]{bak92c}
  \By{Henry~G.~Baker}
  \Work{Metacircular Semantics for {Common Lisp} Special Forms}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1992}
  \IssueVN{5}{4}
  \Pages{11--12}

\bibitem[Bak93]{bak93}
  \By{Henry~G.~Baker}
  \Work{Equal Rights for Functional Objects or,
        The More Things Change, The More They Are the Same}
  \In{{ACM SIGPLAN} {OOPS} Messenger}
  \At{1993}
  \IssueVN{4}{4}
  \Pages{2--27}

\bibitem[Bar84]{bar84}
  \By{Hendrik Pieter Barendregt}
  \Book{The~Lambda Calculus, Its Syntax and Semantics}
  \Published{North Holland}{1984}
  \Numpages{621}
  \VolumeOf{Studies in Logic and the Foundations of Mathematics}{103}

\bibitem[Bar84$'$]{bar84-r}
  \By{Хенк~Барендрегт}
  \Book{Лямбда-исчисление. Его синтаксис и семантика}
  \PublishedAt{М.}{Мир}{1985}
  \Numpages[с.]{606}

\bibitem[Bar89]{bar89}
  \Work{{Scheme$\to$C}, a Portable {Scheme-to-C} Compiler}
  \Report{research report}{WRL-89-1}
  \OfPeopleFrom{DEC Western Research Laboratory}{Joel~F.~Bartlett}
  \At{1989}

\bibitem[Baw88]{baw88}
  \By{Andrew~Bawden}
  \Work{Reification without Evaluation}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{342--349}

\bibitem[BC87]{bc87}
  \By{J.-P.~Briot and P.~Cointe}
  \Work{A~Uniform Model for Object-Oriented Languages Using the Class Abstraction}
  \In{Intern. Joint Conf. on Artificial Intelligence}
  \Volume{1}
  \At{1987}
  \Pages{40--43}

\bibitem[BCSJ86]{bcsj86}
  \By{J.-P.~Briot, P.~Cointe et E.~Saint-James}
  \Work{Re{\'e}criture et r{\'e}cursion dans une fermeture etude dans un {Lisp}
        {\`a} liason superficielle et application aux objets}
  \In{BIGRE+Globule}
  \At{1986}
  \IssueV{48}
  \Pages{90--100}

\bibitem[BDG\+88]{bdg+88}
  \Work{{Common Lisp Object System} Specification}
  \Of{D.~G.~Bobrow, L.~G.~DeMichiel, R.~P.~Gabriel, et~al.}
  \In{{ACM SIGPLAN} Notices}
  \At{1988}
  \IssueV{23}
  \Numpages{142}
  \Note{Spec. iss.}

\bibitem[Bel73]{bel73}
  \By{James~R.~Bell}
  \Work{Threaded Code}
  \In{Communications of the {ACM}}
  \At{1973}
  \IssueVN{16}{6}
  \Pages{370--372}

\bibitem[Bet91]{bet91}
  \By{David~M.~Betz}
  \Book{{XSCHEME}: An Object-Oriented {Scheme}}
  \Published{{P.O. Box 144}, {Peterborough}, {NH 03458} (USA)}{1991}
  \Note{Version 0.28}

\bibitem[BG94]{bg94}
  \By{Henri~Elle~Bal and Dick~Grune}
  \Book{Programming Language Essentials}
  \Published{Addison-Wesley}{1994}
  \Numpages{288}

\bibitem[BHY88]{bhy88}
  \By{A.~Bloss, P.~Hundak, and J.~Young}
  \Work{Code Optimizations for Lazy Evaluation}
  \In{Lisp and Symbolic Computation}
  \At{1988}
  \IssueVN{1}{2}
  \Pages{147--164}

\bibitem[BJ86]{bj86}
  \By{D.~H.~Bartley and J.~C.~Jensen}
  \Work{The~Implementation of {PC~Scheme}}
  \In{Proc. of the 1986 {ACM} Conf. on {LISP} and Functional Programming}
  \At{1986}
  \Pages{86--93}

\bibitem[BKK\+86]{bkk+86}
  \Work{{CommonLoops}: Merging {Lisp} and Object-Oriented Programming}
  \Of{D.~G.~Bobrow, K.~Kahn, G.~Kiczales, et~al.}
  \In{{OOPSLA'86} Conf. Proc. on Object-Oriented Programming Systems, Languages,
      and Applications}
  \At{1986}
  \Pages{17--29}

\bibitem[BM82]{bm82}
  \Work{A~Mechanical Proof of the Unsolvability of the Halting Problem}
  \Report{technical report}{ICSCA-CMP-28}
  \OfPeopleFrom{Institute for Computing Science and
                Computer Applications}{R.~S.~Boyer and J~S.~Moore}
  \At{1982}

\bibitem[BR88]{br88}
  \By{A.~Bawden and J.~Rees}
  \Work{Syntactic Closures}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{86--95}

\bibitem[BW88]{bw88}
  \By{H.-J.~Boehm and M.~Weiser}
  \Work{Garbage Collection in an Uncooperative Environment}
  \In{Software---Practice {\&} Experience}
  \At{1988}
  \IssueVN{18}{9}
  \Pages{807--820}

\bibitem[Car93]{car93}
  \Work{An~implementation of {$F_{<\colon}$}}
  \Report{research report}{97}
  \OfPeopleFrom{DEC Systems Research Center}{Luca~Cardelli}
  \At{1993}

\bibitem[Car94]{car94}
  \By{George~J.~Carrette}
  \Book{{SIOD}: {Scheme} in One Defun}
  \At{1994}

\bibitem[Cay83]{cay83}
  \By{Michel~Cayrol}
  \Book{Le~langage {Lisp}}
  \Published{Cepadues Editions}{1983}
  \Numpages{143}

\bibitem[CC77]{cc77}
  \By{P.~Cousot and R.~Cousot}
  \Work{Abstract Interpretation: A~Unified Lattice Model for Static Analisys of
        Programs by Construction or Approximation of Fixpoints}
  \In{Proc. of the 4th {ACM SIGACT-SIGPLAN} Symp. on Principles of Programming
      Languages}
  \At{1977}
  \Pages{238--252}

\bibitem[CDD\+91]{cdd+91}
  \Work{Le-Lisp version 15.24, Le manuel de r{\'e}f{\'e}rence}
  \OfPeopleFrom{J.~Chailloux, M.~Devin, F.~Dupont, et~al.}{INRIA}
  \At{1991}

\bibitem[CEK\+89]{cek+89}
  \Work{Recommended {C} Style and Coding Standards}
  \Of{L.~W.~Cannon, R.~A.~Elliot, L.~W.~Kirchhoff, et~al.}
  \At{1989}

\bibitem[CG77]{cg77}
  \By{D.~W.~Clark and C.~C.~Green}
  \Work{An~Empirical Study of List Structure in {LISP}}
  \In{Communications of the {ACM}}
  \At{1977}
  \IssueVN{20}{2}
  \Pages{78--87}

\bibitem[CH94]{ch94}
  \By{W.~D.~Clinger and L.~T.~Hansen}
  \Work{Lambda, the Ultimate Label, or A~Simple Optimizing Compiler for {Scheme}}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{128--139}

\bibitem[Cha80]{cha80}
  \By{J{\'e}r{\^o}me~Chailloux}
  \Work{Le~mod{\`e}le {VLISP}\,: description, impl{\'e}mentation et {\'e}valuation}
  \Thesis{th{\`e}se de troisi{\`e}me cycle}
  \From{Unversit{\'e} Paris-VIII}
  \At{1980}

\bibitem[Cha96]{cha96}
  \By{Gregory~J.~Chaitin}
  \Work{The~Limits of Mathematics}
  \In{Journal of Universal Computer Science}
  \At{1996}
  \IssueVN{2}{5}
  \Pages{270--305}

\bibitem[CHO88]{cho88}
  \By{W.~D.~Clinger, A.~H.~Hartheimer, and E.~M.~Ost}
  \Work{Implementation Strategies for Continuations}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{124--131}

\bibitem[Chr95]{chr95}
  \By{Christophe}
  \Book{La~Famille {Fenouillard}}
  \Published{Armand Colin}{1895}

\bibitem[Cla79]{cla79}
  \By{Douglas~W.~Clark}
  \Work{Measurements of Dynamic List Structure Use in {Lisp}}
  \In{{IEEE} Trans. on Software Engineering}
  \At{1979}
  \IssueVN{5}{1}
  \Pages{51--59}

\bibitem[Cli84]{cli84}
  \By{William~D.~Clinger}
  \Work{The~{Scheme}~311 compiler: An~Exercise in Denotational Semantics}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{356--364}

\bibitem[Coi87]{coi87}
  \By{Pierre~Cointe}
  \Work{The~{ObjVlisp} Kernel: A~Reflexive Architecture to Define a Uniform
        Object-Oriented System}
  \In{Workshop on Meta-Level Architecture and Reflection}
  \At{1987}
  \Note{Was not published.}

\bibitem[Com84]{com84}
  \By{Douglas~Comer}
  \Book{Operating System Design: The {XINU} Approach}
  \Published{Prentice-Hall}{1984}
  \Numpages{496}

\bibitem[CR91a]{cr91a}
  \By{W.~Clinger and J.~Rees}
  \Work{Macros that Work}
  \In{Proc. of the 18th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1991}
  \Pages{155--162}

\bibitem[CR91b]{cr91b}
  \Work{Revised\textsuperscript{4} Report on the Algorithmic Language {Scheme}}
  \EditedBy{W.~Clinger and J.~Rees}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1991}
  \IssueVN{4}{3}
  \Numpages{55}

\bibitem[Cur89]{cur89}
  \By{Pavel~Curtis}
  \Work{{(Algorithms)}}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1989}
  \IssueVN{3}{1}
  \Pages{48--61}

\bibitem[Dan87]{dan87}
  \By{Olivier~Danvy}
  \Work{Memory Allocation and Higher-Order Functions}
  \In{Proc. of the {ACM SIGPLAN'87} Symp. on Interpreters and Interpretive
      Techniques}
  \At{1987}
  \Pages{241--252}

\bibitem[Del89]{del89}
  \By{Vincent~Delacour}
  \Work{Picolo expresso}
  \In{BIGRE+Globule}
  \At{1989}
  \IssueN{65}
  \Pages{30--42}

\bibitem[Deu80]{deu80}
  \By{L~Peter~Deutsch}
  \Work{{ByteLisp} and Its {Alto} Implemenatation}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{231--242}

\bibitem[Deu89]{deu89}
  \Work{G{\'e}n{\'e}ration automatique d'interpreteurs et compilation {\`a}
        partir de sp{\'e}cifications d{\'e}notationnelles}
  \Report{rapport de DEA-LAP}{LITP-RXF 89-17}
  \OfPeopleFrom{Laboratoire d'Informatique Th{\'e}orique
                et Programmation}{Alain~Deutsch}
  \At{1989}

\bibitem[Dev85]{dev85}
  \Work{Le~portage du syst\`{e}me Le-Lisp}
  \Report{rapport technique}{50}
  \OfPeopleFrom{INRIA-Rocquencourt}{Matthieu~Devin}
  \At{1985}

\bibitem[DF90]{df90}
  \By{O.~Danvy and A.~Filinski}
  \Work{Abstracting Control}
  \In{Proc. of the 1990 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1990}
  \Pages{151--160}

\bibitem[DFH86]{dfh86}
  \By{R.~K.~Dybvig, D.~P.~Friedman, and C.~T.~Haynes}
  \Work{Expansion-Passing Style: Beyond Conventional Macros}
  \In{Proc. of the 1986 {ACM} Conf. on {LISP} and Functional Programming}
  \At{1986}
  \Pages{143--150}

\bibitem[DFH88]{dfh88}
  \By{R.~K.~Dybvig, D.~P.~Friedman, and C.~T.~Haynes}
  \Work{Expansion-Passing Style: A General Macro Mechanism}
  \In{Lisp and Symbolic Computation}
  \At{1988}
  \IssueVN{1}{1}
  \Pages{53--76}

\bibitem[DH92]{dh92}
  \By{O.~Danvy and J.~Hatcliff}
  \Work{Thunks (continued)}
  \In{Proc. of the 2nd Intern. Workshop on Static Analysis}
  \At{1992}
  \Pages{3--11}
  \Note{See also technical report CIS-92-28, Kansas State University.}

\bibitem[DHB93]{dhb93}
  \By{R.~K.~Dybvig, R.~G.~Hieb, and C.~T.~Bruggerman}
  \Work{Syntactic Abstaction in {Scheme}}
  \In{Lisp and Symbolic Computation}
  \At{1993}
  \IssueVN{5}{4}
  \Pages{295--326}

\bibitem[DHHM92]{dhhm92}
  \Work{Monotonic Conflict Resolution Mechanisms for Inheritance}
  \Of{R.~Ducournau, M.~Habib, M.~Huchard, et~al.}
  \In{{OOPSLA'92} Conf. Proc. on Object-Oriented Programming Systems, Languages,
      and Applications}
  \At{1992}
  \Pages{16--24}

\bibitem[Dil88]{dil88}
  \By{Antoni~Diller}
  \Book{Compiling Functional Languages}
  \Published{John~Wiley~{\&} Sons}{1988}
  \Numpages{322}

\bibitem[DM88]{dm88}
  \Work{A~Blond Primer}
  \Report{rapport}{DIKU 88/21}
  \OfPeopleFrom{University of Copenhagen}{O.~Danvy and K.~Malmkj{\ae}r}
  \At{1988}

\bibitem[DM95]{dm95}
  \By{Antione~Dumesnil de~Maricourt}
  \Work{Macro-expansion en {Lisp}, s{\'e}mantique et r{\'e}lisation}
  \Thesis{th{\`e}se d'universit{\'e}}
  \From{Universit{\'e} Paris-VII}
  \At{1995}

\bibitem[DPS94a]{dps94a}
  \By{H.~Davis, P.~Parquier, and N.~S{\'e}niak}
  \Work{Sweet Harmony: The {Talk/C++} Connection}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{121--127}

\bibitem[DPS94b]{dps94b}
  \By{H.~Davis, P.~Parquier, and N.~S{\'e}niak}
  \Work{Talking About Modules and Delivery}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{113--120}

\bibitem[dR87]{dr87}
  \By{Jim~des~Rivi{\`e}res}
  \Work{Control-Related Meta-Level Facilities in {Lisp}}
  \In{Workshop on Meta-Level Architecture and Reflection}
  \At{1987}
  \Pages{101--110}

\bibitem[dRS84]{drs84}
  \By{J.~des~Rivi{\`e}res and B.~C.~Smith}
  \Work{The~Implemenatation of Procedurally Reflective Languages}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{331--347}

\bibitem[Dyb87]{dyb87}
  \By{R.~Kent~Dybvig}
  \Book{The~{SCHEME} Programming Language}
  \Published{Prentice-Hall}{1987}
  \Numpages{242}

\bibitem[ES70]{es70}
  \By{J.~Earley and H.~Sturgis}
  \Work{A~Formalism for Translator Interaction}
  \In{Communications of the {ACM}}
  \At{1970}
  \IssueVN{13}{10}
  \Pages{607--617}

\bibitem[Fel88]{fel88}
  \By{Matthias~Felleisen}
  \Work{The~Theory and Practice of First-Class Prompts}
  \In{Proc. of the 15th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1988}
  \Pages{180--190}

\bibitem[Fel90]{fel90}
  \By{Matthias~Felleisen}
  \Work{On the Expressive Power of Programming Languages}
  \In{ESOP'90 Selected Papers from the Symp. on the 3rd European Symposium on
      Programming}
  \At{1990}
  \Pages{134--151}

\bibitem[FF87]{ff87}
  \By{M.~Felleisen and D.~P.~Friedman}
  \Work{A~Reduction Semantics for Imperative Higher-Order Languages}
  \In{Parallel Architectures and Languages {Europe}}
  \Volume{II}
  \At{1987}
  \Pages{206-223}

\bibitem[FF89]{ff89}
  \By{M.~Felleisen and D.~P.~Friedman}
  \Work{A~Syntactic Theory of Sequential State}
  \In{Theoretical Computer Science}
  \At{1989}
  \IssueVN{69}{3}
  \Pages{243--287}

\bibitem[FFDM87]{ffdm87}
  \Work{Beyond Continuations}
  \Report{technical report}{TR216}
  \OfPeopleFrom{Indiana University, Computer Science Dept.}{M.~Felleisen,
                D.~P.~Friedman, B.~Duba, et~al.}
  \At{1987}

\bibitem[FH89]{fh89}
  \Work{The~Revised Report on the Syntactic Theories of Sequential
        Control and State}
  \Report{technical report}{100-89}
  \OfPeopleFrom{Rice University}{M.~Felleisen and R.~Hieb}
  \At{1989}

\bibitem[FL87]{fl87}
  \By{M.~Feeley and G.~LaPalme}
  \Work{Using Closures for Code Generation}
  \In{Computer Languages}
  \At{1987}
  \IssueVN{12}{1}
  \Pages{47--66}

\bibitem[FM90]{fm90}
  \By{M.~Feeley and J.~S.~Miller}
  \Work{A~Parallel Virtual Machine for Efficient {Scheme} Compilation}
  \In{Proc. of the 1990 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1990}
  \Pages{119--130}

\bibitem[FW76]{fw76}
  \By{D.~P.~Friedman and D.~S.~Wise}
  \Work{{CONS} Should Not Evaluate Its Arguments}
  \In{Proc. of the 3rd Intern. Colloquium on Automata, Languages and Programming}
  \At{1976}
  \Pages{257--284}

\bibitem[FW84]{fw84}
  \By{D.~P.~Friedman and M.~Wand}
  \Work{Reification: Reflection Without Metaphysics}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{348--355}

\bibitem[FWFD88]{fwfd88}
  \Work{Abstract Continuations: A Mathematical Semantics for Handling Functional
        Jumps}
  \Of{M.~Felleisen, M.~Wand, D.~P.~Friedman, et~al.}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{52--62}

\bibitem[FWH92]{fwh92}
  \By{Daniel~P.~Friedman, Mitchell~Wand, and Christopher~T.~Haynes}
  \Book{Essentials of Programming Languages}
  \Published{MIT Press and McGraw-Hill}{1992}
  \Numpages{536}

\bibitem[Gab88]{gab88}
  \By{Richard~P.~Gabriel}
  \Work{The~Why of {Y}}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1988}
  \IssueVN{2}{2}
  \Pages{15--25}

\bibitem[GBM82]{gbm82}
  \By{M.~L.~Griss, E.~Benson, and G.~Q.~Maguire~Jr}
  \Work{{PSL}: A~Portable {LISP} System}
  \In{Proc. of the 1982 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1982}
  \Pages{88--97}

\bibitem[Gor75]{gor75}
  \Work{Operational Reasoning and Denotational Semantics}
  \Report{research report}{STAN-CS-506}
  \OfPeopleFrom{Stanford University, Computer Science Dept.}{Michael~Gordon}
  \At{1975}

\bibitem[Gor88]{gor88}
  \By{Michael~Gordon}
  \Book{Programming Language Theory and its Implemenatation}
  \Published{Prentice-Hall}{1988}
  \Numpages{255}
  \Series{International Series in Computer Science}

\bibitem[GP88]{gp88}
  \By{R.~P.~Gabriel and K.~M.~Pitman}
  \Work{Technical Issues of Separation in Function Cells and Value Cells}
  \In{Lisp and Symbolic Computation}
  \At{1988}
  \IssueVN{1}{1}
  \Pages{81--101}

\bibitem[GR83]{gr83}
  \By{Ad{\`e}le~Goldberg and David~Robson}
  \Book{{Smalltalk"~80}: The Language and its Implemenatation}
  \Published{Addison-Wesley}{1983}
  \Numpages{714}

\bibitem[Gra93]{gra93}
  \By{Paul~Graham}
  \Book{On~{Lisp}: Advanced Techniques for {Common Lisp}}
  \Published{Prentice-Hall}{1993}
  \Numpages{413}

\bibitem[Gre77]{gre77}
  \By{Patrick~Greussay}
  \Work{Contribution {\`a} la d{\'e}finiton interpr{\`e}tative et {\`a}
        l'impl{\'e}mentation des Lambda-langages}
  \Thesis{th{\`e}se d'{\'e}tat}
  \From{Unversit{\'e} Paris-VI}
  \At{1977}

\bibitem[Gud93]{gud93}
  \Work{Representing Type Information in Dynamically Typed Languages}
  \Report{technical report}{93-27}
  \OfPeopleFrom{University of Arizona, Dept. of Computer Science}{David~Gudeman}
  \At{1993}

\bibitem[Han90]{han90}
  \By{Chris~Hanson}
  \Work{Efficient Stack Allocation for Tail-Recursive Languages}
  \In{Proc. of the 1990 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1990}
  \Pages{106--118}

\bibitem[HD90]{hd90}
  \By{R.~Hieb and R.~K.~Dybvig}
  \Work{Continuations and Concurrency}
  \In{Proc. of the 2nd {ACM SIGPLAN} Symp. on Principles {\&} Practice of
      Parallel Programming}
  \At{1990}
  \Pages{128--136}

\bibitem[HDB90]{hdb90}
  \By{R.~Hieb, R.~K.~Dybvig, and C.~Bruggerman}
  \Work{Representing Control in the Presence of First-Class Continuations}
  \In{Proc. of the {ACM SIGPLAN'90} Conf. on Programming Language Design and
      Implementation}
  \At{1990}
  \Pages{66--77}

\bibitem[Hen80]{hen80}
  \By{Peter~Henderson}
  \Book{Functional Programming: Application and Implementation}
  \Published{Prentice-Hall}{1980}
  \Numpages{350}
  \Series{International Series in Computer Science}

\bibitem[Hen80$'$]{hen80-r}
  \By{Питер~Хендерсон}
  \Book{Функциональное программирование. Применение и реализация}
  \PublishedAt{М.}{Мир}{1983}
  \Numpages[с.]{349}
  \Series{Математическое обеспечение ЭВМ}

\bibitem[Hen92a]{hen92a}
  \By{Fritz~Henglein}
  \Work{Global Tagging Optimizations by Type Inference}
  \In{Proc. of the 1992 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1992}
  \Pages{205--215}

\bibitem[Hen92b]{hen92b}
  \By{Wade~Henessey}
  \Work{{WCL}: Delivering Efficient {Common Lisp} Applications Under {\UNIX}}
  \In{Proc. of the 1992 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1992}
  \Pages{260-269}

\bibitem[HFW84]{hfw84}
  \By{C.~T.~Haynes, D.~P.~Friedman, and M.~Wand}
  \Work{Continuations and Coroutines}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{293-298}

\bibitem[Hof93]{hof93}
  \By{Ulrich~Hoffmann}
  \Work{Using {C} as Target Code for Translating High-Level Programming Languages}
  \In{Journal of {C} Language Translation}
  \At{1993}
  \IssueVN{5}{2}
  \Pages{70--90}

\bibitem[Hon93]{hon93}
  \By{P.~Joseph~Hong}
  \Work{Threaded Code Designs for {Forth} Interpreters}
  \In{{ACM SIGFORTH} Newsletter}
  \At{1993}
  \IssueVN{4}{2}
  \Pages{11--16}

\bibitem[HS75]{hs75}
  \By{C.~Hewitt and B.~Smith}
  \Work{Towards a Programming Apprentice}
  \In{{IEEE} Trans. on Software Engineering}
  \At{1975}
  \IssueVN{1}{1}
  \Pages{26--45}

\bibitem[HS91]{hs91}
  \By{Samuel~P.~Harbison and Guy~Lewis~{Steele~Jr}}
  \Book{{C}: A~Reference Manual}
  \Edition{3rd edition}
  \Published{Prentice-Hall}{1991}
  \Numpages{392}

\bibitem[IEE91]{iee91}
  \Standard{{IEEE} 1178-1990}
  \Book{{IEEE} Standard for the {Scheme} Programming Language}
  \Published{Institute of Electrical and Electronic Engineers}{1991}

\bibitem[ILO94]{ilo94}
  \Work{{Ilog Talk} Reference Manual}
  \From{ILOG}
  \At{1994}

\bibitem[IM89]{im89}
  \By{Takayasu~Ito and Manabu~Matsui}
  \Work{A~Parallel {Lisp} Language PaiLisp and Its Kernel Specification}
  \In{Proc. of the {US/Japan} Workshop on Parallel {Lisp}: Languages and Systems}
  \At{1989}
  \Pages{58--100}

\bibitem[IMY92]{imy92}
  \By{Yuuju~Ichisugi, Satoshi~Matsuoka, and Akinori~Yonezawa}
  \Work{{RbCL}: A Reflective Object-Oriented Concurrent Language without a
        Run-Time Kernel}
  \In{Proc. of Intern. Workshop on New Models for Software Architecture}
  \At{1992}
  \Pages{24--35}

\bibitem[ISO90]{iso90}
  \Standard{{ISO/IEC} 9899:1990}
  \Book{Programming Languages~--~{C}}
  \Published{International Organization for Standardization}{1990}

\bibitem[ISO94]{iso94}
  \Standard{{ISO/IEC} {JTC1/SC22/WG16}}
  \Book{Programming Language {ISLISP}}
  \Published{International Organization for Standardization}{1994}

\bibitem[ITW86]{itw86}
  \By{Takayasu~Ito, Takashi~Tamura, and Shinichi~Wada}
  \Work{Theoretical Comparisons of Interpreted/Compiled Executions of {Lisp}
        on Sequential and Parallel Machine Models}
  \In{Proc. of the {IFIP} 10th World Computer Congress}
  \At{1986}
  \Pages{349--354}

\bibitem[Jaf94]{jaf94}
  \By{Aubrey~Jaffer}
  \Book{Reference Manual for {SCM}}
  \At{1994}

\bibitem[JF92]{jf92}
  \By{S.~Jefferson and D.~P.~Friedman}
  \Work{A~Simple Reflective Interpreter}
  \In{Proc. of Intern. Workshop on New Models for Software Architecture}
  \At{1992}
  \Pages{48--58}

\bibitem[JGS93]{jgs93}
  \By{Neil~D.~Jones, Carsten~K.~Gomard, and Peter~Sestoft}
  \Book{Partial Evaluation and Automatic Program Generation}
  \Published{Prentice-Hall}{1993}
  \Numpages{400}
  \Series{International Series in Computer Science}
  \Note{With chapters by L.~O.~Andersen and T.~Mogensen.}

\bibitem[Kah87]{kah87}
  \By{Gilles~Kahn}
  \Work{Natural Semantics}
  \In{Proc. of the 4th Annual Symp. on Theoretical Aspects of Computer Science}
  \At{1987}
  \Pages{22--39}

\bibitem[Kam90]{kam90}
  \By{Samuel~N.~Kamin}
  \Book{Programming Languages: An Interpreter-Based Approach}
  \Published{Addison-Wesley}{1990}
  \Numpages{640}

\bibitem[KCR98]{kcr98}
  \Work{Revised\textsuperscript{5} Report on the Algorithmic Language {Scheme}}
  \EditedBy{R.~Kelsey, W.~Clinger, and J.~Rees}
  \In{{ACM SIGPLAN} Notices}
  \At{1998}
  \IssueVN{33}{9}
  \Numpages{50}

\bibitem[KdRB92]{kdrb92}
  \By{Gregor~Kiczales, Jim~des~Rivi{\`e}res, and Daniel~G.~Bobrow}
  \Book{The~Art of the Metaobject Protocol}
  \Published{MIT Press}{1992}
  \Numpages{345}

\bibitem[Kes88]{kes88}
  \By{Robert~R.~Kessler}
  \Book{{Lisp}, Objects, and Symbolic Programming}
  \Published{Scott~Foresman~{\&}~Co}{1988}
  \Numpages{644}

\bibitem[KFFD86]{kffd86}
  \Work{Hygienic Macro Expansion}
  \Of{E.~E.~Kohlbecker, D.~P.~Friedman, M.~Felleisen, et~al.}
  \In{Proc. of the 1986 {ACM} Conf. on {LISP} and Functional Programming}
  \At{1986}
  \Pages{151--161}

\bibitem[KH89]{kh89}
  \By{R.~Kelsey and P.~Hudak}
  \Work{Realistic Compilation by Program Transformation}
  \In{Proc. of the 16th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1989}
  \Pages{281--292}

\bibitem[Knu84]{knu84}
  \By{Donald~Ervin~Knuth}
  \Book{The~{\TeX}book}
  \Published{Addison-Wesley}{1984}
  \Numpages{496}

\bibitem[Knu84$'$]{knu84-r}
  \By{Дональд~Эрвин~Кнут}
  \Book{Всё про {\TeX}}
  \Published{Вильямс}{2003}
  \Numpages[с.]{560}
  \Series{Компьютеры и вёрстка}

\bibitem[KR78]{kr78}
  \By{Brian~W.~Kernighan and Dennis~M.~Ritchie}
  \Book{The~{C} Programming Language}
  \Published{Prentice-Hall}{1978}
  \Numpages{228}

\bibitem[KR90]{kr90}
  \By{G.~Kiczales and L.~Rodriguez}
  \Work{Efficient Method Dispatch in {PCL}}
  \In{Proc. of the 1990 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1990}
  \Pages{99--105}

\bibitem[KW90]{kw90}
  \By{M.~Katz and D.~Weise}
  \Work{Continuing into the Future: On the Interaction of Futures and
        First-Class Continuations}
  \In{Proc. of the 1990 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1990}
  \Pages{176--184}

\bibitem[Lak80]{lak80}
  \By{Fred~H.~Lakin}
  \Work{Computing with Text-Graphical Forms}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{100--106}

\bibitem[Lan65]{lan65}
  \By{Peter~J.~Landin}
  \Work{Correspondence between {ALGOL 60} and {Church's} Lambda-notation}
  \In{Communications of the {ACM}}
  \At{1965}
  \IssueV{8}
  \Pages{89--101 and 158--165}

\bibitem[Leb05]{leb05}
  \By{Maurice~Leblanc}
  \Book{813}
  \Published{{\'E}ditions Pierre Lafitte}{1905}

\bibitem[LF88]{lf88}
  \By{H.~Lieberman and C.~Fry}
  \Work{Common {EVAL}}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1988}
  \IssueVN{2}{1}
  \Pages{23--33}

\bibitem[LF93]{lf93}
  \By{S.-D.~Lee and D.~P.~Friedman}
  \Work{Quasi-Static Scoping: Sharing Variable Bindings Across Multiple Lexical
        Scopes}
  \In{Proc. of the 20th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1993}
  \Pages{479--492}

\bibitem[Lie87]{lie87}
  \By{Henry~Lieberman}
  \Work{Reversible Object-Oriented Interpreters}
  \In{Proc. of the {ECOOP'87} European Conf. on Object-Oriented Programming}
  \At{1987}
  \Pages{11--19}

\bibitem[LLSt93]{llst93}
  \Work{{GNU} {Emacs Lisp} Reference Manual}
  \OfPeopleFrom{B.~Lewis, D.~LaLiberte, R.~Stallman,
                and {GNU} Manual Group}{Free Software Foundation}
  \Edition{2nd~edition}
  \At{1993}

\bibitem[LP86]{lp86}
  \By{K.~J.~Lang and B.~A.~Pearlmutter}
  \Work{{Oaklisp}: An Object-Oriented {Scheme} with First Class Types}
  \In{{OOPSLA'86} Conf. Proc. on Object-Oriented Programming Systems, Languages,
      and Applications}
  \At{1986}
  \Pages{30--37}

\bibitem[LP88]{lp88}
  \By{K.~J.~Lang and B.~A.~Pearlmutter}
  \Work{{Oaklisp}: An Object-Oriented Dialect of {Scheme}}
  \In{Lisp and Symbolic Computation}
  \At{1988}
  \IssueVN{1}{1}
  \Pages{39--51}

\bibitem[LW93]{lw93}
  \By{Xavier~Leroy et Pierre~Weis}
  \Book{Manuel de r{\'e}f{\'e}rence du langage {Caml}}
  \Published{Inter{\'E}ditions}{1993}

\bibitem[MAE\+62]{mae+62}
  \Work{{LISP 1.5} Programmer's Manual}
  \Of{John~McCarthy, Paul~W.~Abrahams, Daniel~J.~Edwards, et~al.}
  \Published{MIT Press}{1962}
  \Numpages{112}

\bibitem[Man74]{man74}
  \By{Zohar~Manna}
  \Book{Mathematical Theory of Computation}
  \Published{McGraw-Hill}{1974}
  \Numpages{448}
  \Series{Computer Science Series}

\bibitem[Mas86]{mas86}
  \By{Ian~A.~Mason}
  \Book{The~Semantics of Destructive {LISP}}
  \Published{CSLI}{1986}
  \Numpages{300}
  \Series{Lecture notes}

\bibitem[Mat92]{mat92}
  \By{Luis~Mateu}
  \Work{An~Efficient Implemenatation of Coroutines}
  \In{Proc. of the {IWMM'92} Intern. Workshop on Memory Management}
  \At{1992}
  \Pages{230--247}

\bibitem[MB93]{mb93}
  \By{Luis~Mateu-Brule}
  \Work{Strat{\'e}gies avanc{\'e}es pour la gestion de blocs de contr{\^o}le}
  \Thesis{th{\`e}se de doctorat d'universit{\'e}}
  \From{Unversit{\'e} Paris-VI}
  \At{1993}

\bibitem[McC60]{mcc60}
  \By{John~McCarthy}
  \Work{Recursive Functions of Symbolic Expressions and Their Computation by
        Machine, {Part~I}}
  \In{Communications of the {ACM}}
  \At{1960}
  \IssueVN{3}{1}
  \Pages{184--195}

\bibitem[McC78a]{mcc78a}
  \By{John~McCarthy}
  \Work{History of {LISP}}
  \In{{ACM SIGPLAN} Notices}
  \At{1978}
  \IssueVN{13}{8}
  \Pages{217--223}

\bibitem[McC78b]{mcc78b}
  \By{John~McCarthy}
  \Work{A~micro-manual for {LISP}~-- Not the whole truth}
  \In{{ACM SIGPLAN} Notices}
  \At{1978}
  \IssueVN{13}{8}
  \Pages{215--216}

\bibitem[McD93]{mcd93}
  \Work{The~Relatedness and Comparative Utility of Various Approaches
        to Operational Semantics}
  \Report{technical report}{MS-CIS-93-16}
  \OfPeopleFrom{University of Pennsylvaina, CIS~Dept.}{Raymond~McDowell}
  \At{1993}

\bibitem[MNC\+89]{mnc+89}
  \Work{Les langages {\`a} objets}
  \Of{G{\'e}rald~Masini, Amedeo~Napoli, Dominique~Colnet, et~al.}
  \Published{Inter{\'E}ditions}{1989}

\bibitem[MNC\+89$'$]{mnc+89-e}
  \Work{Object-Oriented Languages}
  \Of{G{\'e}rald~Masini, Amedeo~Napoli, Dominique~Colnet, et~al.}
  \Published{Academic Press}{1991}
  \Numpages{512}

\bibitem[Mor92]{mor92}
  \By{Luc~Moreau}
  \Work{An~Operational Semantics for a Parallel Functional Language with Continuations}
  \In{Proc. of the 4th Intern. Conf. on Parallel Architectures and Languages {Europe}}
  \At{1992}
  \Pages{415--420}

\bibitem[Mor94]{mor94}
  \By{Luc~Moreau}
  \Work{Sound Evaluation of Parallel Functional Programs with First-Class Continuations}
  \Thesis{PhD thesis}
  \From{University of Li{\`e}ge}
  \At{1994}

\bibitem[Mos70]{mos70}
  \By{Joel~Moses}
  \Work{The~Function of FUNCTION in {LISP}, or Why the {FUNARG} Problem Should
        be Called the Environment Problem}
  \In{{ACM SIGSAM} Bulletin}
  \At{1970}
  \IssueN{15}
  \Pages{13--27}

\bibitem[Moz87]{moz87}
  \By{Вольфганг~Амадей~Моцарт}
  \Work{Дон Жуан}
  \Type{опера}
  \At{1787}

\bibitem[MP80]{mp80}
  \By{S.~S.~Muchnick and U.~F.~Pleban}
  \Work{A~Semantic Comparison of {LISP} and {Scheme}}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{56--65}

\bibitem[MQ94]{mq94}
  \By{L.~Moreau and C.~Queinnec}
  \Work{Partial Continuations as the Difference of Continuations~-- A~Duumvirate
        of Control Operators}
  \In{Proc. of the 6th Intern. Symp. on Programming Language Implementation and
      Logic Programming}
  \At{1994}
  \Pages{182--197}

\bibitem[MR91]{mr91}
  \By{J.~S.~Miller and G.~J.~Rozas}
  \Work{Free Variables and First-Class Environments}
  \In{Lisp and Symbolic Computation}
  \At{1991}
  \IssueVN{4}{2}
  \Pages{107--141}

\bibitem[MS80]{ms80}
  \By{F.~L.~Morris and J.~S.~Schwarz}
  \Work{Computing Cyclic List Structures}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{144--153}

\bibitem[Mul92]{mul92}
  \By{Robert~Muller}
  \Work{{M-Lisp}: A Representation-Independent Dialect of {Lisp} with Reduction
        Semantics}
  \In{{ACM} Trans. on Programming Languages and Systems}
  \At{1992}
  \IssueVN{14}{4}
  \Pages{589--615}

\bibitem[Nei84]{nei84}
  \By{Eugen~Neidl}
  \Work{{\'E}tude des relations avec l'interpr{\`e}te dans la compilation de {Lisp}}
  \Thesis{Th{\`e}se de troisi{\`e}me cycle}
  \From{Unversit{\'e} Paris-VI}
  \At{1984}

\bibitem[Nor72]{nor72}
  \By{Eric J. Norman}
  \Book{{1100 LISP} Reference Manual}
  \Published{University of Wisconsin}{1972}

\bibitem[NQ89]{nq89}
  \Work{Identifier Semantics: A Matter of References}
  \Report{technical report}{LIX RR 89 02}
  \OfPeopleFrom{Laboratoire d'Informatique
                de l'{\'E}cole Polytechnique}{G.~Nuyens and C.~Queinnec}
  \At{1989}
  \Pages{67--80}

\bibitem[PE92]{pe92}
  \Work{The~\textsc{EuLisp} Definition}
  \EditedBy{J.~Padget and G.~Nuyens.}
  \At{1992}

\bibitem[Per79]{per79}
  \By{Jean-Fran{\c c}ois~Perrot}
  \Work{{Lisp} et $\lambda$-calcul}
  \In{Actes de la 6e {\'e}cole de printemps d'informatique th{\'e}orique}
  \At{1979}
  \Pages{277--301}

\bibitem[Pit80]{pit80}
  \By{Kent~Pitman}
  \Work{Special Forms in {LISP}}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{179--187}

\bibitem[PJ87]{pj87}
  \By{Simon~L.~Peyton-Jones}
  \Book{The~Implemenatation of Functional Programming Languages}
  \Published{Prentice-Hall}{1987}
  \Numpages{500}
  \Series{International Series in Computer Science}

\bibitem[PNB93]{pnb93}
  \By{J.~Padget, G.~Nuyens, and H.~Bretthauer}
  \Work{An~Overview of \textsc{EuLisp}}
  \In{Lisp and Symbolic Computation}
  \At{1993}
  \IssueVN{6}{1/2}
  \Pages{9--98}

\bibitem[QC88]{qc88}
  \By{C.~Queinnec and P.~Cointe}
  \Work{An~Open-Ended Data Representation Model for \textsc{EuLisp}}
  \In{Proc. of the 1988 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1988}
  \Pages{298--308}

\bibitem[QD93]{qd93}
  \By{C.~Queinnec and D.~DeRoure}
  \Work{Design of a concurrent and distributed language}
  \In{Proc. of the {US/Japan} Workshop on Parallel Symbolic Computing:
      Languages, Systems, and Applications}
  \At{1993}
  \Pages{234--259}

\bibitem[QD96]{qd96}
  \By{C.~Queinnec and D.~DeRoure}
  \Work{Sharing Code through First-Class Environments}
  \In{Proc. of the 1996 {ACM SIGPLAN} Intern. Conf. on Functional Programming}
  \At{1996}
  \Pages{251--261}

\bibitem[QG92]{qg92}
  \By{C.~Queinnec and J.-M.~Geffroy}
  \Work{Partial Evaluation Applied to Symbolic Pattern Matching with Intelligent
        Backtrack}
  \In{Actes {WSA'92} Workshop on Static Analysis {(Bordeaux)}}
  \At{1992}
  \Pages{109--117}

\bibitem[QP90]{qp90}
  \Work{A~Deterministic Model for Modules and Macros}
  \Report{technical report}{90-36}
  \OfPeopleFrom{University of Bath,
                Bath Computing Group}{C.~Queinnec and J.~Padget}
  \At{1990}

\bibitem[QP91a]{qp91a}
  \By{C.~Queinnec and J.~Padget}
  \Work{A~Proposal for a Modular {Lisp} with Macros and Dynamic Evaluation}
  \In{Journ{\'e}es de Travail sur l'Analyse Statique en Programmation
      {\'E}quationnelle, Fonctionnelle et Logique}
  \At{1991}
  \Pages{1--8}

\bibitem[QP91b]{qp91b}
  \By{C.~Queinnec and J.~Padget}
  \Work{Modules, Macros and {Lisp}}
  \In{The~11th Intern. Conf. of the {Chilean} Computer Science Society}
  \At{1991}
  \Pages{111--123}

\bibitem[QS91]{qs91}
  \By{C.~Queinnec and B.~Serpette}
  \Work{A~Dynamic Extent Control Operator for Partial Continuations}
  \In{Proc. of the 18th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1991}
  \Pages{174--184}

\bibitem[Que82]{que82}
  \By{Christian~Queinnec}
  \Book{Langage d'un autre type\,: {LISP}}
  \Published{Eyrolles}{1982}
  \Numpages{184}

\bibitem[Que89]{que89}
  \Work{{Lisp}~--\,Almost a whole Truth!}
  \Report{technical report}{LIX RR 89 03}
  \OfPeopleFrom{Laboratoire d'Informatique
                de l'{\'E}cole Polytechnique}{Christian~Queinnec}
  \At{1989}
  \Pages{79--105}

\bibitem[Que90a]{que90a}
  \By{Christian~Queinnec}
  \Work{A~Framework for Data Aggregates}
  \In{Actes des {JFLA} 90 -- Journ{\'e}es Francophones des Langages Applicatifs}
  \At{1990}
  \Pages{21--32}

\bibitem[Que90b]{que90b}
  \By{Christian~Queinnec}
  \Book{Le~filtrage\,: une application de (et~pour) {Lisp}}
  \Published{Inter{\'E}ditions}{1990}
  \Numpages{201}

\bibitem[Que90c]{que90c}
  \By{Christian~Queinnec}
  \Work{{PolyScheme}: A Semantics for a Concurrent {Scheme}}
  \In{High Performance and Parallel Computing in {Lisp}}
  \At{1990}

\bibitem[Que92a]{que92a}
  \By{Christian~Queinnec}
  \Work{Compiling Syntactically Recursive Programs}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1992}
  \IssueVN{5}{4}
  \Pages{2--10}

\bibitem[Que92b]{que92b}
  \By{Christian~Queinnec}
  \Work{A~Concurrent and Distributed Extension of {Scheme}}
  \In{Proc. of the 4th Intern. Conf. on Parallel Architectures and Languages {Europe}}
  \At{1992}
  \Pages{431--446}

\bibitem[Que93a]{que93a}
  \By{Christian~Queinnec}
  \Work{Continuation Conscious Compilation}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1993}
  \IssueVN{6}{1}
  \Pages{2--14}

\bibitem[Que93b]{que93b}
  \By{Christian~Queinnec}
  \Work{Designing {\textsc{Meroon}~V3}}
  \In{{ECOOP'93} Workshop on Object-Oriented Programming in {Lisp}: Languages
      and Applications}
  \At{1993}

\bibitem[Que93c]{que93c}
  \By{Christian~Queinnec}
  \Work{A~Library of High-Level Control Operators}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1993}
  \IssueVN{6}{4}
  \Pages{11--26}

\bibitem[Que93d]{que93d}
  \Work{Literate Programming from {Scheme} to {\TeX}}
  \Report{research report}{LIX RR 93 05}
  \OfPeopleFrom{Laboratoire d'Informatique
                de l'{\'E}cole Polytechnique}{Christian~Queinnec}
  \Pages{79--105}
  \At{1993}

\bibitem[Que94]{que94}
  \By{Christian~Queinnec}
  \Work{Locality, Causality and Continuations}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{91--102}

\bibitem[Que95]{que95}
  \By{Christian~Queinnec}
  \Work{\textsc{DMeroon}. Overview of a Distributed Class-based
        Causality-coherent Data Model}
  \In{Proc. of the Intern. Workshop {PSLS'95} on Parallel Symbolic Languages and
      Systems}
  \At{1995}
  \Pages{297--309}

\bibitem[R3R86]{r3r86}
  \Work{Revised\textsuperscript{3} Report on the Algorithmic Language {Scheme}}
  \EditedBy{W.~Clinger and J.~Rees}
  \In{{ACM SIGPLAN} Notices}
  \At{1986}
  \IssueVN{21}{12}
  \Pages{37--79}

\bibitem[RA82]{ra82}
  \By{J.~A.~Rees and N.~I.~Adams}
  \Work{{T}: A~Dialect of {Lisp} or, {LAMBDA}: The Ultimate Software Tool}
  \In{Proc. of the 1982 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1982}
  \Pages{114--122}

\bibitem[RAM84]{ram84}
  \By{J.~A.~Rees, N.~I.~Adams, and J.~R. Meehan}
  \Work{The~{T} Manual}
  \Of{Yale University, Computer Science Dept.}
  \Edition{4th edition}
  \At{1984}

\bibitem[Ray91]{ray91}
  \By{Eric Raymond}
  \Book{The~New Hacker's Dictionary}
  \Published{MIT Press}{1991}

\bibitem[Rey72]{rey72}
  \By{John~C.~Reynolds}
  \Work{Definitional Interpreters for Higher-Order Programming Languages}
  \In{Proc. of the {ACM} Annual Conference}
  \At{1972}
  \Pages{717--740}

\bibitem[Rib69]{rib69}
  \By{Daniel~Ribbens}
  \Book{Programmation non num{\'e}rique\,: {LISP~1.5}}
  \Published{Dunod}{1969}
  \Series{Monographies d'Informatique}

\bibitem[RM92]{rm92}
  \By{J.~R.~Rose and H.~Muller}
  \Work{Integrating the {Scheme} and {C} Languages}
  \In{Proc. of the 1992 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1992}
  \Pages{247--259}

\bibitem[Row80]{row80}
  \By{William~Rowan}
  \Work{A~{LISP} Compiler Producing Compact Code}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{216--222}

\bibitem[Roz92]{roz92}
  \By{Guillermo~Juan~Rozas}
  \Work{Taming the {Y} Operator}
  \In{Proc. of the 1992 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1992}
  \Pages{226--234}

\bibitem[Sam79]{sam79}
  \By{Hanan~Sammet}
  \Work{Deep and Shallow Binding: The Assignment Operation}
  \In{Computer Languages}
  \At{1979}
  \IssueV{4}
  \Pages{187--198}

\bibitem[Sch86]{sch86}
  \By{David~Schmidt}
  \Book{Denotational Semantics: A~Methodology for Language Development}
  \Published{Allyn and Bacon}{1986}
  \Numpages{348}

\bibitem[Sco76]{sco76}
  \By{Dana~Scott}
  \Work{Data Types as Lattices}
  \In{SIAM Journal on Computing}
  \At{1976}
  \IssueVN{5}{3}
  \Pages{522--587}

\bibitem[S{\'e}n89]{sen89}
  \By{Nitsan~S{\'e}niak}
  \Work{Compilation de Scheme par sp{\'e}cialisation explicite}
  \In{BIGRE+Globule}
  \At{1989}
  \IssueN{65}
  \Pages{160--170}

\bibitem[S{\'e}n91]{sen91}
  \By{Nitsan~S{\'e}niak}
  \Work{Th{\'e}orie et practique de {Sqil}, un langage interm{\'e}diare pour la
        compilation des langages fonctionnels}
  \Thesis{th{\`e}se de doctorat d'universit{\'e}}
  \From{Unversit{\'e} Paris-VI}
  \At{1991}

\bibitem[Ser93]{ser93}
  \By{Manuel~Serrano}
  \Work{De~l'utilisation des analyses de flot de contr{\^o}le dans la
        compilation des langages fonctionnels}
  \In{Actes des journ{\'e}es du {GDR} de Programmation}
  \At{1993}
  \Pages{226--234}
  \Note{See also PLILP'94 proc., P.~447--448.}

\bibitem[Ser94]{ser94}
  \By{Manuel~Serrano}
  \Book{{Bigloo's} User Manual}
  \At{1994}

\bibitem[SF89]{sf89}
  \By{George~Springer and Daniel~P.~Friedman}
  \Book{{Scheme} and the Art of Programming}
  \Published{MIT Press}{1989}
  \Numpages{600}

\bibitem[SF92]{sf92}
  \By{A.~Sabry and M.~Felleisen}
  \Work{Reasoning About Programs in Continuation-Passing Style}
  \In{Proc. of the 1992 {ACM} Conf. on {Lisp} and Functional Programming}
  \At{1992}
  \Pages{288--298}

\bibitem[SG93]{sg93}
  \By{G.~L.~{Steele~Jr} and R.~P.~Gabriel}
  \Work{The~Evolution of {Lisp}}
  \In{{ACM SIGPLAN} Notices}
  \At{1993}
  \IssueVN{28}{3}
  \Pages{231--270}

\bibitem[Shi91]{shi91}
  \By{Olin~Shivers}
  \Work{Data-flow Analysis and Type Recovery in {Scheme}}
  \PartOf{Topics in Advanced Language Implemenatation}
  \EditedBy{Peter~Lee.}
  \Published{MIT Press}{1991}

\bibitem[SJ87]{sj87}
  \By{Emmanuel~Saint-James}
  \Work{De~la m{\'e}ta-r{\'e}cursivit{\'e} comme outil d'impl{\'e}mentation}
  \Thesis{th{\`e}se d'{\'e}tat}
  \From{Unversit{\'e} Paris-VI}
  \At{1987}

\bibitem[SJ93]{sj93}
  \By{Emmanuel~Saint-James}
  \Book{La~programmation applicative (de {LISP} {\`a}~la machine en passant par
        le lambda-calcul)}
  \Published{Herm{\`e}s}{1993}
  \Numpages{411}

\bibitem[Sla61]{sla61}
  \By{James~R.~Slagle}
  \Work{A~Heuristic Program that Solves Symbolic Integration Problems in
        Freshman Calculus, Symbolic Automatic Integration {(SAINT)}}
  \Thesis{PhD thesis}
  \From{MIT, Dept. of Mathematics}
  \At{1961}

\bibitem[Spi90]{spi90}
  \By{{\'E}ric~Spir}
  \Book{Gestion dynamique de la m{\'e}moire dans les langages de programmation,
        application {\`a} {Lisp}}
  \Published{Inter{\'E}ditions}{1990}
  \Numpages{156}
  \Series{Science informatique}

\bibitem[SS75]{ss75}
  \Work{{Scheme}: An Interpreter for Extended Lambda Сalculus}
  \Report{AI~Memo}{349}
  \OfPeopleFrom{Massachusetts Institute of
                Technology}{G.~J.~Sussman and G.~L.~{Steele~Jr}}
  \At{1975}

\bibitem[SS78a]{ss78a}
  \Work{The~Art of the Interpreter or The Modularity Complex
        (Parts Zero, One, and~Two)}
  \Report{AI~Memo}{453}
  \OfPeopleFrom{Massachusetts Institute of
                Technology}{G.~L.~{Steele~Jr} and G.~J.~Sussman}
  \At{1978}

\bibitem[SS78b]{ss78b}
  \Work{The~Revised Report on {SCHEME}, a~Dialect of {LISP}}
  \Report{AI~Memo}{452}
  \OfPeopleFrom{Massachusetts Institute of
                Technology}{G.~L.~{Steele~Jr} and G.~J.~Sussman}
  \At{1978}

\bibitem[SS80]{ss80}
  \By{G.~L.~{Steele~Jr} and G.~J.~Sussman}
  \Work{The~Dreams of Lifetime: A Lazy Variable Extent Mechanism}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{163--172}

\bibitem[Ste78]{ste78}
  \Work{{RABBIT}: A~Compiler for {SCHEME}}
  \Report{AI~Memo}{474}
  \OfPeopleFrom{Massachusetts Institute of Technology}{Guy~Lewis~{Steele~Jr}}
  \At{1978}

\bibitem[Ste84]{ste84}
  \By{Guy~Lewis~{Steele~Jr}}
  \Book{\textsc{Common Lisp}. The Language}
  \Published{Digital Press}{1984}
  \Numpages{465}

\bibitem[Ste90]{ste90}
  \By{Guy~Lewis~{Steele~Jr}}
  \Book{\textsc{Common Lisp}. The Language}
  \Edition{2nd~edition}
  \Published{Digital Press}{1990}
  \Numpages{1029}

\bibitem[Sto77]{sto77}
  \By{Joseph~E.~Stoy}
  \Book{Denotational Semantics: The {Scott-Strachey} Approach to Programming
        Language Theory}
  \Published{MIT Press}{1977}
  \Numpages{414}

\bibitem[Str86]{str86}
  \By{Bjarne~Stroustrup}
  \Book{The~{C++} Programming Language}
  \Published{Addison-Wesley}{1986}
  \Numpages{326}

\bibitem[SW94]{sw94}
  \By{M.~Serrano and P.~Weis}
  \Work{$1 + 1 = 1$: An Optimizing {Caml} Compiler}
  \In{Record of the 1994 {ACM SIGPLAN} Workshop on {ML} and Its Applications}
  \At{1994}
  \Pages{101--111}

\bibitem[Tak88]{tak88}
  \By{Masato~Takeichi}
  \Work{Lambda-Hoisting: A~Transformation Technique for Fully Lazy
         Evaluation of Functional Programs}
  \In{New Generation Computing}
  \At{1988}
  \IssueVN{5}{4}
  \Pages{377--391}

\bibitem[Tei74]{tei74}
  \By{Warren~Teitelman}
  \Work{{InterLISP} Reference Manual}
  \Of{Xerox Palo Alto Research Center}
  \At{1974}

\bibitem[Tei76]{tei76}
  \By{Warren~Teitelman}
  \Work{{CLisp}: Coversational {LISP}}
  \In{{IEEE} Trans. on Computers}
  \At{1976}
  \IssueVN{25}{4}
  \Pages{354--357}

\bibitem[VH94]{vh94}
  \By{J.~Vitek and R.~N.~Horspool}
  \Work{Taming Message Passing: Efficient Method Look-Up for Dynamically Typed
        Languages}
  \In{Proc. of the 8th European Conf. on Object-Oriented Programming}
  \At{1994}
  \Pages{432--449}

\bibitem[Wad88]{wad88}
  \By{Philip~Wadler}
  \Work{Deforestation: Transforming Programs to Eliminate Trees}
  \In{Proc. of the 2nd European Symposium on Programming}
  \At{1988}
  \Pages{344--358}

\bibitem[Wan80a]{wan80a}
  \By{Mitchell~Wand}
  \Work{Continuation-Based Multiprocessing}
  \In{Proc. of the 1980 {ACM} {LISP} Conference}
  \At{1980}
  \Pages{19--28}

\bibitem[Wan80b]{wan80b}
  \By{Mitchell~Wand}
  \Work{Continuation-Based Program Transformation Strategies}
  \In{Journal of the {ACM}}
  \At{1980}
  \IssueVN{27}{1}
  \Pages{164--180}

\bibitem[Wan84]{wan84}
  \By{Mitchell~Wand}
  \Work{A~Semantic Prototyping System}
  \In{Proc. of the 1984 {SIGPLAN} Symp. on Compiler Construction}
  \At{1984}
  \Pages{213--221}

\bibitem[Wan86]{wan86}
  \By{M.~Wand and D.~P.~Friedman}
  \Work{The~Mystery of the Tower Revealed: A Non-Reflective Description of the
        Reflective Tower}
  \In{Proc. of the 1986 {ACM} Conf. on {LISP} and Functional Programming}
  \At{1986}
  \Pages{298--307}

\bibitem[Wat93]{wat93}
  \By{Richard~C.~Waters}
  \Work{\textsc{Macroexpand-All}: An Example of a Simple {Lisp} Code Walker}
  \In{{ACM SIGPLAN} Lisp Pointers}
  \At{1993}
  \IssueVN{6}{1}
  \Pages{25--32}

\bibitem[WC94]{wc94}
  \By{A.~K.~Wright and R.~Cartwright}
  \Work{A~Practical Soft Type System for {Scheme}}
  \In{Proc. of the 1984 {ACM} Symp. on {LISP} and Functional Programming}
  \At{1984}
  \Pages{250--262}

\bibitem[WH89]{wh89}
  \By{Patrick~H.~Winston and Berthold~K.~Horn}
  \Book{LISP}
  \Edition{3rd edition}
  \Published{Addison-Wesley}{1989}
  \Numpages{611}

\bibitem[Wil92]{wil92}
  \By{Paul~R.~Wilson}
  \Work{Uniprocessor Garbage Collection Techniques}
  \In{Proc. of the {IWMM'92} Intern. Workshop on Memory Management}
  \At{1992}
  \Pages{1--42}

\bibitem[WL93]{wl93}
  \By{Pierre~Weis et Xavier~Leroy}
  \Book{Le~langage {Caml}}
  \Published{Inter{\'E}ditions}{1993}

\bibitem[WS91]{ws91}
  \By{Larry~Wall and Randal~L.~Schwartz}
  \Book{Programming {Perl}}
  \Published{O'Reilly Media}{1991}
  \Numpages{482}

\bibitem[WS94]{ws94}
  \By{M.~Wand and P.~Steckler}
  \Work{Selective and Lightweight Closure Conversion}
  \In{Proc. of the 21th {ACM SIGPLAN-SIGACT} Symp. on Principles of Programming
      Languages}
  \At{1994}
  \Pages{435--445}

\bibitem[YH85]{yh85}
  \By{Taiichi~Yuasa and Masami~Hagiya}
  \Work{{Kyoto Common Lisp} Report}
  \From{Kyoto University}
  \At{1985}

\bibitem[YS92]{ys92}
  \Work{Proceedings of International Workshop on New Models for Software
        Architecture: Reflection and Meta-Level Architecture}
  \EditedBy{Akinori~Yonezawa and Brian~C.~Smith.}
  \PublishedAt{Tokyo}{RISE}{1992}

\end{thebibliography}
